\bfseries Riemann Normal Coordinate expansions using Cadabra

### 2019-09-24 source/tex/paper.tex
Fixed one typo in paper.tex
What can I say?

The following results were obtained from equation \eqref{eqn:RabcdPartials}. Note that by
inspection of these reulst and those above it is easy to verify the claim made in
section (\ref{sec:MetricRNC}) that the connection terms that arise in
$R^{a}{}_{(bc{\Dot d};\ue)}$ are always of the form $\Gamma^{p}{}_{q(r,\us)}$.
%
\begin{dgroup*}[compact,spread={3pt}]
   \dMath{11.13}{    R^a{}_{(cd{\Dot b},e)} = \cdb{dRabcd61}}{eqn:dRabcd61}{\hfill}
   \dMath{11.14}{    R^a{}_{(cd{\Dot b},ef)} = \cdb{dRabcd62}}{eqn:dRabcd62}{\hfill}
   \dMath{11.15}{ -2 R^a{}_{(cd{\Dot b},efg)} = \cdb{dRabcd63}}{eqn:dRabcd63}{\hfill}
   \dMath{11.16}{ -5 R^a{}_{(cd{\Dot b},efgh)} = \cdb{dRabcd64}}{eqn:dRabcd64}{\hfill}
   \dMath{11.17}{ -3 R^a{}_{(cd{\Dot b},efghi)} = \cdb{dRabcd65}}{eqn:dRabcd65}{\hfill}
\end{dgroup*}

>>>>

The following results were obtained from equation \eqref{eqn:RabcdPartials}. Note that by
inspection of these results and those above it is easy to verify the claim made in
section (\ref{sec:MetricRNC}) that the connection terms that arise in
$R^{a}{}_{(bc{\Dot d};\ue)}$ are always of the form $\Gamma^{p}{}_{q(r,\us)}$.
%
\begin{dgroup*}[compact,spread={3pt}]
   \dMath{11.13}{    R^a{}_{(cd{\Dot b},e)} = \cdb{dRabcd61}}{eqn:dRabcd61}{\hfill}
   \dMath{11.14}{    R^a{}_{(cd{\Dot b},ef)} = \cdb{dRabcd62}}{eqn:dRabcd62}{\hfill}
   \dMath{11.15}{ -2 R^a{}_{(cd{\Dot b},efg)} = \cdb{dRabcd63}}{eqn:dRabcd63}{\hfill}
   \dMath{11.16}{ -5 R^a{}_{(cd{\Dot b},efgh)} = \cdb{dRabcd64}}{eqn:dRabcd64}{\hfill}
   \dMath{11.17}{ -3 R^a{}_{(cd{\Dot b},efghi)} = \cdb{dRabcd65}}{eqn:dRabcd65}{\hfill}
\end{dgroup*}
